### 2025-05-08 Chapters/paper1.tex
changes

>>>>

\begin{algorithm}
	\textbf{Input:} raw\_fname, annot\_fname, load\_eeg\_only, crop\_wake\_mins\\
	\textbf{Output:} raw\\

	mapping $\gets$ \{'EOG horizontal': 'eog', \dots\}\\
	exclude $\gets$ mapping.keys() \textbf{if} load\_eeg\_only \textbf{then do nothing}\\
	raw $\gets$ read\_raw\_edf(raw\_fname, exclude)\\
	annots $\gets$ read\_annotations(annot\_fname)\\
	raw.set\_annotations(annots)\\
	\textbf{if} not load\_eeg\_only \textbf{then}\\
	\hspace{1cm} raw.set\_channel\_types(mapping)\\
	\textbf{if} crop\_wake\_mins > 0 \textbf{then}\\
	\hspace{1cm} mask $\gets$ [x[-1] in \{'1','2','3','4','R'\} for x in annots.description]\\
	\hspace{1cm} inds $\gets$ where(mask)\\
	\hspace{1cm} tmin $\gets$ annots[inds[0]].onset - crop\_wake\_mins * 60\\
	\hspace{1cm} tmax $\gets$ annots[inds[-1]].onset + crop\_wake\_mins * 60\\
	\hspace{1cm} raw.crop(tmin, tmax)\\
	rename EEG channel names\\
	subj\_nb $\gets$ int(fname[3:5]), rec\_nb $\gets$ int(fname[5])\\
	raw.info.subject\_info $\gets$ \{id: subj\_nb, rec\_id: rec\_nb\}\\
	\textbf{Return} raw\\
	\caption{load\_sleep\_physionet\_raw}
\end{algorithm}

\begin{algorithm}
	\textbf{Input:} fnames, l\_freq, h\_freq\\
	\textbf{Output:} raws\\

	raws $\gets$ [load\_sleep\_physionet\_raw(f[0], f[1]) for f in fnames]\\
	\textbf{for each} raw \textbf{in} raws \textbf{do}\\
	\hspace{1cm} raw.load\_data()\\
	\hspace{1cm} raw.filter(l\_freq, h\_freq)\\
	\textbf{Return} raws\\
	\caption{Load and Filter All Files}
\end{algorithm}

\begin{algorithm}
	\textbf{Input:} raw\_data\_list, epoch\_length = 30\\
	\textbf{Output:} epochs\_list, labels\\

	epochs\_list $\gets$ [\,]\\
	labels $\gets$ [\,]\\
	\textbf{for each} raw \textbf{in} raw\_data\_list \textbf{do}\\
	\hspace{1cm} sfreq $\gets$ int(raw.info['sfreq'])\\
	\hspace{1cm} (events, event\_ids) $\gets$ events\_from\_annotations(raw)\\
	\hspace{1cm} sleep\_ids $\gets$ [1,2,3,4,5]\\
	\hspace{1cm} filtered\_events $\gets$ [event for event in events if event[2] in sleep\_ids]\\
	\hspace{1cm} filtered\_event\_ids $\gets$ \{k:v for k,v in event\_ids.items() if v in sleep\_ids\}\\
	\hspace{1cm} filtered\_events $\gets$ np.array(filtered\_events, dtype=int)\\
	\hspace{1cm} epochs $\gets$ Epochs(raw, filtered\_events, filtered\_event\_ids, 0, epoch\_length - 1/sfreq)\\
	\hspace{1cm} epochs\_list.append(epochs)\\
	\hspace{1cm} labels.extend([event[2] for event in filtered\_events])\\
	\textbf{Return} epochs\_list, labels\\
	\caption{Epoch Creation}
\end{algorithm}

\begin{algorithm}
	\textbf{Input:} epochs\_list, labels\\
	\textbf{Output:} model performance metrics\\

	(epochs\_list, labels) $\gets$ create\_epochs(raws)\\
	X $\gets$ concatenate([epochs.get\_data() for epochs in epochs\_list], axis=0)\\
	(n\_epochs, n\_channels, n\_times) $\gets$ X.shape\\
	X $\gets$ reshape(X, (n\_epochs, n\_channels * n\_times))\\
	y $\gets$ np.array(labels)\\
	(X\_resampled, y\_resampled) $\gets$ SMOTE().fit\_resample(X, y)\\
	(X\_train, X\_test, y\_train, y\_test) $\gets$ train\_test\_split(X\_resampled, y\_resampled, 0.2)\\
	model $\gets$ initialize\_ML\_model()\\
	model.fit(X\_train, y\_train)\\
	y\_pred $\gets$ model.predict(X\_test)\\
	report $\gets$ classification\_report(y\_test, y\_pred)\\
	cm $\gets$ confusion\_matrix(y\_test, y\_pred)\\
	display(report)\\
	display\_confusion\_matrix(cm)\\
	\caption{ML Training and Evaluation Pipeline}
\end{algorithm}

	\begin{algorithm}
		\textbf{Input:} list of (signal\_file, annotation\_file) pairs \\
		\textbf{Output:} average accuracy, classification report, confusion matrix

		\vspace{0.3cm}
		\texttt{epochs\_list = []} \\
		\texttt{for file\_pair in fnames:} \\
		\hspace*{0.5cm}\texttt{raw = read\_raw\_edf(file\_pair[0])} \\
		\hspace*{0.5cm}\texttt{annot = read\_annotations(file\_pair[1])} \\
		\hspace*{0.5cm}\texttt{raw.set\_annotations(annot)} \\
		\hspace*{0.5cm}\texttt{annot.crop(annot[1].onset - 1800, annot[-2].onset + 1800)} \\
		\hspace*{0.5cm}\texttt{events = events\_from\_annotations(raw)} \\
		\hspace*{0.5cm}\texttt{epochs = Epochs(raw, events)} \\
		\hspace*{0.5cm}\texttt{epochs\_list.append(epochs)} \\

		\vspace{0.3cm}
		\texttt{all\_epochs = concatenate\_epochs(epochs\_list)} \\
		\texttt{y = all\_epochs.events[:, 2]} \\

		\vspace{0.3cm}
		\textbf{Define feature extraction:} \\
		\texttt{def eeg\_power\_band(epochs):} \\
		\hspace*{0.5cm}\texttt{psds = compute\_psd(epochs)} \\
		\hspace*{0.5cm}\texttt{psds = normalize(psds)} \\
		\hspace*{0.5cm}\texttt{features = []} \\
		\hspace*{0.5cm}\texttt{for band in freq\_bands:} \\
		\hspace*{1cm}\texttt{features.append(mean\_psd\_in\_band)} \\
		\hspace*{0.5cm}\texttt{return concatenate(features)} \\

		\vspace{0.3cm}
		\textbf{Train ML pipeline with KFold:} \\
		\texttt{pipeline = [eeg\_power\_band, Classifier()]} \\
		\texttt{kf = KFold(n\_splits=5)} \\
		\texttt{results = \{\}} \\
		\texttt{for train\_idx, test\_idx in kf.split(all\_epochs):} \\
		\hspace*{0.5cm}\texttt{X\_train = all\_epochs[train\_idx]} \\
		\hspace*{0.5cm}\texttt{X\_test = all\_epochs[test\_idx]} \\
		\hspace*{0.5cm}\texttt{y\_train = y[train\_idx]} \\
		\hspace*{0.5cm}\texttt{y\_test = y[test\_idx]} \\
		\hspace*{0.5cm}\texttt{pipeline.fit(X\_train, y\_train)} \\
		\hspace*{0.5cm}\texttt{y\_pred = pipeline.predict(X\_test)} \\
		\hspace*{0.5cm}\texttt{store accuracy, y\_true, y\_pred} \\

		\caption{General ML Pipeline with K-Fold Cross-Validation}
	\end{algorithm}
